---
title: "The Avengers: NBA Playoffs"
author: "Samad Patel"
date: "8/27/2018"
output: pdf_document
---

```{r Relevant Packages and Functions, echo=FALSE, message=FALSE, warning=FALSE}
library(dplyr)
library(readr)
library(splashr)
library(docker)
library(rvest)
library(stringr)
library(curl)
source('~/Desktop/NBA Snap Project/Code/Final_Snap_Functions.R')
```


Peter Parker is gone. We've had enough time to deal with it. Let's focus on the real issues - how would the NBA Playoffs have turned out if half of each roster was snapped? This module serves to investigate that. 

# Snapping the Players 

The first step is to collect the rosters of the playoffs teams, and then remove half of them. For the sake of argument, we will say LeBron James is Thanos (only due to the LeThanos memes at /r/NBA). He remains on the Cavs by default. With the exception of LeBron, each player has close to a 50% chance of remaining on the team. 

```{r Snap, echo=FALSE, warning=FALSE, message=FALSE}
# FULL ROSTERS - EAST
# Cavs vs Pacers
cle_roster <- read_csv("~/Desktop/NBA Snap Project/Rosters/cavaliers.csv", 
                      skip = 8, col_names = c('Player'))
ind_roster <- read_csv("~/Desktop/NBA Snap Project/Rosters/pacers.csv", 
                      skip = 8, col_names = c('Player'))

# Celtics vs Bucks
bos_roster <- read_csv("~/Desktop/NBA Snap Project/Rosters/celtics.csv", 
                    skip = 8, col_names = c('Player'))
mil_roster <- read_csv("~/Desktop/NBA Snap Project/Rosters/bucks.csv", 
                    skip = 8, col_names = c('Player'))

# Raptors vs Wizards
was_roster <- read_csv("~/Desktop/NBA Snap Project/Rosters/wizards.csv", 
                    skip = 8, col_names = c('Player'))
tor_roster <- read_csv("~/Desktop/NBA Snap Project/Rosters/raptors.csv", 
                    skip = 8, col_names = c('Player'))

# 76rs vs Heat
phi_roster <- read_csv("~/Desktop/NBA Snap Project/Rosters/phil.csv", 
                 skip = 8, col_names = c('Player'))
mia_roster <- read_csv("~/Desktop/NBA Snap Project/Rosters/heat.csv", 
                 skip = 8, col_names = c('Player'))

# Function to clean names and snap players
snap <- function(df){
   df[,1] <- gsub("\\\\.*", '', df$Player)
   # Return random sample of half the players, round up 
   df <- df[sample(1:nrow(df), ceiling(nrow(df)/2)), ]
   return(df$Player)
}

# Rewrite each team name with the snap 
set.seed(1500)
for (team in ls()[sapply(mget(ls()), is.data.frame)]){
   assign(team, snap(get(team)))
}

print('Eastern Conference Rosters:')
tibble(bos_roster, cle_roster, ind_roster, mia_roster, mil_roster, phi_roster, tor_roster, was_roster)
```

# Eastern Conference First Round
## Celtics Vs. Bucks

```{r, echo=FALSE}
load("~/Desktop/NBA Snap Project/PreLoadedData.RData")
urls <- c('https://www.basketball-reference.com/boxscores/201804150BOS.html',
          'https://www.basketball-reference.com/boxscores/201804170BOS.html',
          'https://www.basketball-reference.com/boxscores/201804200MIL.html',
          'https://www.basketball-reference.com/boxscores/201804220MIL.html',
          'https://www.basketball-reference.com/boxscores/201804240BOS.html',
          'https://www.basketball-reference.com/boxscores/201804260MIL.html',
          'https://www.basketball-reference.com/boxscores/201804280BOS.html')
Determine_Series(urls = urls, Team1_Abb = 'mil', Team2_Abb = 'bos')
```
Game one was extremely close, with games 2 and 3 being won decisively. The next three games were extremely close but Boston won the series with a nail-biter Game 7 at home! 

## Cavaliers Vs. Pacers
```{r, echo=FALSE}
urls <- c('https://www.basketball-reference.com/boxscores/201804150CLE.html',
         'https://www.basketball-reference.com/boxscores/201804180CLE.html',                                 'https://www.basketball-reference.com/boxscores/201804200IND.html',
         'https://www.basketball-reference.com/boxscores/201804220IND.html',
         'https://www.basketball-reference.com/boxscores/201804250CLE.html',
         'https://www.basketball-reference.com/boxscores/201804270IND.html',
         'https://www.basketball-reference.com/boxscores/201804290CLE.html')
Determine_Series(urls = urls, Team1_Abb = 'ind', Team2_Abb = 'cle')
```

This series shows the limitations of the algorithm. The Pacers take it with extremely lopsided victories in 5 games. LeThanos plays his last game as a Cavalier with a loss at home. After scoring 40 points in the first 28 minutes and barely keeping the game close, he decided to sub out after which the Cavs were outscored 100-9. The something of decisions requires the something of wills blah blah find a new slant. 

## Heat Vs. 76rs 
```{r, echo=FALSE}
load("~/Desktop/NBA Snap Project/PreLoadedData.RData")
# Last two games come from regular season - closest two games to playoffs 
urls = c('https://www.basketball-reference.com/boxscores/201804140PHI.html',
         'https://www.basketball-reference.com/boxscores/201804160PHI.html',
         'https://www.basketball-reference.com/boxscores/201804190MIA.html',
         'https://www.basketball-reference.com/boxscores/201804210MIA.html',
         'https://www.basketball-reference.com/boxscores/201804240PHI.html',
         'https://www.basketball-reference.com/boxscores/201803080MIA.html',
         'https://www.basketball-reference.com/boxscores/201802270MIA.html')
Determine_Series(urls = urls, Team1_Abb = 'mia', Team2_Abb = 'phi')
```

Another brutally competitive and physical series, Philadelphia takes Game 6. In the soul stone, Whiteside insists he would have led the Heat to win in 4. 

## Wizards Vs. Raptors
```{r, echo=FALSE}
urls = c('https://www.basketball-reference.com/boxscores/201804140TOR.html',
         'https://www.basketball-reference.com/boxscores/201804170TOR.html',
         'https://www.basketball-reference.com/boxscores/201804200WAS.html',
         'https://www.basketball-reference.com/boxscores/201804220WAS.html',
         'https://www.basketball-reference.com/boxscores/201804250TOR.html',
         'https://www.basketball-reference.com/boxscores/201804270WAS.html',
         'https://www.basketball-reference.com/boxscores/201711190TOR.html')
Determine_Series(urls = urls, Team1_Abb = 'was', Team2_Abb = 'tor')
```

Exhilarating series. Toronto took a heavy 2-0 lead with exceptionally lopsided blowouts. Washington came back for a strong showing in Game 3, proving that this wouldn't be a clean sweep. Games 4 and 5 were close, with Toronto losing them away and being blown out in Game 6. They went home with the series tied for an exceptional Game 7 victory. The post-game narrative on Reddit is that Toronto would have choked Game 7 away if DeRozan were playing. 

# Eastern Conference Semi-Finals
## Celtics Vs. 76rs
```{r, echo=FALSE}
urls = c('https://www.basketball-reference.com/boxscores/201804300BOS.html',
         'https://www.basketball-reference.com/boxscores/201805030BOS.html',
         'https://www.basketball-reference.com/boxscores/201805050PHI.html',
         'https://www.basketball-reference.com/boxscores/201805070PHI.html',
         'https://www.basketball-reference.com/boxscores/201805090BOS.html',
         'https://www.basketball-reference.com/boxscores/201801110PHI.html',
         'https://www.basketball-reference.com/boxscores/201801180BOS.html')
Determine_Series(urls = urls, Team1_Abb = 'bos', Team2_Abb = 'phi')
```

Another exhilarating series. Boston took a 2-0 lead after exceptionally close games. They were forced into OT during Game 3 in Philadelphia (and for the sake of excitement we'll say Philly took it). Philly proceeded to take another one at home in a strong Game 4 showing, but Boston took it again in a close Game 5. With elimination on the line, Philadelphia loses by 22 at home after Simmons says fuck it and starts chuckng up 3's. 

## Raptors Vs. Pacers
```{r, echo=FALSE}
urls = c('https://www.basketball-reference.com/boxscores/201712010TOR.html',
         'https://www.basketball-reference.com/boxscores/201711240IND.html',
         'https://www.basketball-reference.com/boxscores/201803150IND.html',
         'https://www.basketball-reference.com/boxscores/201804060TOR.html')
Determine_Series(urls, 'tor', 'ind')
```

In a heavy four game sweep, the Toronto Raptors go on to the Eastern Conference Finals. This might be their year! 

# Eastern Conference Finals
## Celtics Vs. Raptors
```{r, echo=FALSE}
urls = c('https://www.basketball-reference.com/boxscores/201802060TOR.html',
         'https://www.basketball-reference.com/boxscores/201711120BOS.html',
         'https://www.basketball-reference.com/boxscores/201804040TOR.html',
         'https://www.basketball-reference.com/boxscores/201803310BOS.html')
Determine_Series(urls, 'bos', 'tor')
```
```{r, echo = FALSE}
# The series above is 2-2, requiring a tiebreaker 
TieBreaker(urls[4], 'tor', 'bos')
```
For the first time in history, the Toronto Raptors are the Eastern Conference Champions! 

# Western Conference Snap
```{r, warning=FALSE, message=FALSE, echo=FALSE}
# FULL ROSTERS - WEST
# Timberwolves vs Rockets
min_roster <- read_csv("~/Desktop/NBA Snap Project/Rosters/Timberwolves.csv", 
                       skip = 9, col_names = c('Player'))
# hou_roster <- read_csv("~/Desktop/NBA Snap Project/Rosters/Rockets.csv", 
#                 skip = 9, col_names = c('Player'))

# Thunder vs Jazz
uta_roster <- read_csv("~/Desktop/NBA Snap Project/Rosters/Jazz.csv", 
                       skip = 9, col_names = c('Player'))
okc_roster <- read_csv("~/Desktop/NBA Snap Project/Rosters/Thunder.csv", 
                       skip = 9, col_names = c('Player'))

# Trailblazers vs Pelicans
por_roster <- read_csv("~/Desktop/NBA Snap Project/Rosters/Trailblazers.csv", 
                       skip = 9, col_names = c('Player'))
nop_roster <- read_csv("~/Desktop/NBA Snap Project/Rosters/Pelicans.csv", 
                       skip = 9, col_names = c('Player'))

# Warriors vs Spurs
gsw_roster <- read_csv("~/Desktop/NBA Snap Project/Rosters/Warriors.csv", 
                       skip = 9, col_names = c('Player'))
sas_roster <- read_csv("~/Desktop/NBA Snap Project/Rosters/Spurs.csv", 
                       skip = 9, col_names = c('Player'))
# Rewrite each team name with the snap 
set.seed(1300)
for (team in ls()[sapply(mget(ls()), is.data.frame)]){
   assign(team, snap(get(team)))
}

# The Rockets are unique - they only had a 14 team roster - we still want them to have 8 players
# Must snap manually
hou_roster <- read_csv("~/Desktop/NBA Snap Project/Rosters/Rockets.csv", 
                       skip = 9, col_names = c('Player'))
hou_roster <- gsub('\\\\.*', '', hou_roster$Player)
set.seed(1300)
hou_roster <- sample(hou_roster, size = 8)

print('Western Conference Rosters:')
tibble(min_roster, hou_roster, sas_roster, gsw_roster, nop_roster, por_roster, uta_roster, okc_roster)
```

# Western Conference First Round
## Timberwolves Vs. Rockets
```{r, echo=FALSE}
load("~/Desktop/NBA Snap Project/PreLoadedData.RData")
urls = c('https://www.basketball-reference.com/boxscores/201804150HOU.html', 
         'https://www.basketball-reference.com/boxscores/201804180HOU.html',
         'https://www.basketball-reference.com/boxscores/201804210MIN.html',
         'https://www.basketball-reference.com/boxscores/201804230MIN.html',
         'https://www.basketball-reference.com/boxscores/201804250HOU.html',
         'https://www.basketball-reference.com/boxscores/201803180MIN.html', 
         'https://www.basketball-reference.com/boxscores/201802230HOU.html')
Determine_Series(urls, 'min', 'hou')
```

After the Timberwolves take a relatively close victory in Houston for Game 1, the Rockets respond with an absurd performance in Game 2. The Timberwolves pull off another relatively close victory, this time at home, prompting another beatdown by Houston. But after CP3's hamstring goes out on him in Game 5 (in this universe it happens earlier, shut up), Minnesota pulls it together for a hell of a Game 6, and a close Game 7 after Houston misses 27 3-pointers in a row. 

## Thunder Vs. Jazz
```{r, echo=FALSE}
urls = c('https://www.basketball-reference.com/boxscores/201804150OKC.html', 
         'https://www.basketball-reference.com/boxscores/201804180OKC.html',
         'https://www.basketball-reference.com/boxscores/201804210UTA.html',
         'https://www.basketball-reference.com/boxscores/201804230UTA.html',
         'https://www.basketball-reference.com/boxscores/201804250OKC.html',
         'https://www.basketball-reference.com/boxscores/201804270UTA.html',
         'https://www.basketball-reference.com/boxscores/201712200OKC.html')
Determine_Series(urls, 'okc', 'uta')
```
OKC didn't make it out of the snap with PG13, Westbrook, or Melo, so Utah naturally jingled the hell out of OKC in 4. 

## Trailblazers Vs. Pelicans
```{r, echo=FALSE}
urls = c('https://www.basketball-reference.com/boxscores/201804140POR.html',
         'https://www.basketball-reference.com/boxscores/201804170POR.html',
         'https://www.basketball-reference.com/boxscores/201804190NOP.html',
         'https://www.basketball-reference.com/boxscores/201804210NOP.html',
         'https://www.basketball-reference.com/boxscores/201712020POR.html',
         'https://www.basketball-reference.com/boxscores/201803270NOP.html',
         'https://www.basketball-reference.com/boxscores/201710240POR.html')
Determine_Series(urls, 'por', 'nop')
```

I don't know enough about either of these teams to be amusing. Portland in 6. 

## Warriors Vs. Spurs
```{r, echo=FALSE}
urls = c('https://www.basketball-reference.com/boxscores/201804140GSW.html',
         'https://www.basketball-reference.com/boxscores/201804160GSW.html',
         'https://www.basketball-reference.com/boxscores/201804190SAS.html',
         'https://www.basketball-reference.com/boxscores/201804220SAS.html',
         'https://www.basketball-reference.com/boxscores/201804240GSW.html',
         'https://www.basketball-reference.com/boxscores/201711020SAS.html',
         'https://www.basketball-reference.com/boxscores/201802100GSW.html')
Determine_Series(urls, 'sas', 'gsw')
```

Absolutely incredible - even with Steph, Klay, and KD, the Warriors blew a 3-0 lead. Reports indicate that KD was sighted in the parking lot after Game 7 calling LeBron to team up with the Lakers in the fall. 

# Western Conference Semi-Finals
## Timberwolves Vs. Jazz
```{r, echo = FALSE}
urls = c('https://www.basketball-reference.com/boxscores/201803020UTA.html',
         'https://www.basketball-reference.com/boxscores/201804010MIN.html',
         'https://www.basketball-reference.com/boxscores/201711130UTA.html',
         'https://www.basketball-reference.com/boxscores/201710200MIN.html')
Determine_Series(urls, 'min', 'uta')
```

Jazz takes 3 out of the 4 - with Mitchell at the helm, Jazz fans are even more confident that Mitchell will win ROTY. 

## Spurs Vs. Trailblazers
```{r, echo = FALSE}
urls = c('https://www.basketball-reference.com/boxscores/201801070POR.html',
         'https://www.basketball-reference.com/boxscores/201804070SAS.html',
         'https://www.basketball-reference.com/boxscores/201712200POR.html')
Determine_Series(urls, 'por', 'sas')
```

The Spurs take the first 2, and therefore the series. After Manu and Parker were snapped, Spurs fans felt uncertain as far as what the future would hold. It seems like things will be okay after all. 

# Western Conference Finals
## Spurs Vs. Jazz
```{r, echo=FALSE}
urls = c('https://www.basketball-reference.com/boxscores/201802120UTA.html',
         'https://www.basketball-reference.com/boxscores/201803230SAS.html',
         'https://www.basketball-reference.com/boxscores/201712210UTA.html',
         'https://www.basketball-reference.com/boxscores/201802030SAS.html')
Determine_Series(urls, 'sas', 'uta')
```

```{r, echo=FALSE}
TieBreaker(urls[4], 'uta', 'sas')
```

The Utah Jazz are the Western Conference Champions! 

# NBA Finals
```{r, echo = FALSE}
urls = c('https://www.basketball-reference.com/boxscores/201801260TOR.html',
         'https://www.basketball-reference.com/boxscores/201711030UTA.html')
Determine_Series(urls, 'tor', 'uta')
```

In a long and tremendous 2 game-series, the Utah Jazz win their first NBA title! 