---
title: "Scraping (Outside of Written Functions)"
author: "Samad Patel"
date: "8/21/2018"
output: pdf_document
---
```{r Packages, echo=FALSE, message=FALSE, warning=FALSE}
library(readr)
library(dplyr)
library(rvest)
library(docker)
library(splashr)
library(stringr)
```

This document will contain all the relevant code for scraping and data cleaning that is done outside of any user-written functions. 

Much of this is completed using splashr and docker. My Python isn't configured such that R can access the needed containers directly, so there is some command line code being run outside of this document. That which is entered into the command line will be commented. 

## 1) Abbreviations
```{r}
page <- read_html('https://en.wikipedia.org/wiki/Wikipedia:WikiProject_National_Basketball_Association/National_Basketball_Association_team_abbreviations')
Abbs <- page %>% html_nodes('td') %>% html_text()
Abbrevs <- str_replace_all(string = Abbs[seq(3,length(Abbs), by=2)], pattern = '\\n',
                           replacement = '')
FullNames <- str_replace_all(Abbs[seq(4, length(Abbs), by = 2)], pattern = '\\n', 
                             replacement = '')
abbs_df <- data.frame('Abbreviation' = Abbrevs, 'Franchise' = FullNames, stringsAsFactors = FALSE)
```


## 2) Possessions Per Game
```{r Poss Per Game, warning=FALSE, message=FALSE}
# docker run -p 8050:8050 -p 5023:5023 scrapinghub/splash
page <- render_html(url = 'https://www.teamrankings.com/nba/stat/possessions-per-game')
PossPerGame <- page %>% html_nodes('#DataTables_Table_0') %>% html_table()
PossPerGame <- PossPerGame[[1]]
PossPerGame <- PossPerGame %>% select(Team, `2017`, Home, Away)
# Franchise names are very inconvenient for cleaning
PossPerGame$Team <- c('NOP', 'LAL', 'PHX', 'PHI', 'BKN', 'GSW', 'LAC', 'CHI', 'CHA', 'ATL', 
          'ORL', 'TOR', 'DEN', 'OKC', 'NYK', 'WAS', 'HOU', 'POR', 'MIA', 'CLE', 
          'MIL', 'DET', 'MIN', 'BOS', 'UTA', 'DAL', 'IND', 'MEM', 'SAC', 'SAS')
head(PossPerGame)
```

## 3) Opponent's Points Per Game
```{r}
page <- render_html(url = 'https://www.basketball-reference.com/leagues/NBA_2018.html')
OPtsPerGame <- page %>% html_nodes('#opponent-stats-per_game') %>% html_table()
OPtsPerGame <- OPtsPerGame[[1]]
OPtsPerGame <- OPtsPerGame %>% select(Team, PTS)
# Remove the stars
OPtsPerGame$Team <- str_replace_all(OPtsPerGame$Team, '\\*', '')
# Remove league average
OPtsPerGame <- OPtsPerGame[1:30, ]
# Replaces team names with abbreviations 
OPtsPerGame$Team <- abbs_df$Abbreviation[match(OPtsPerGame$Team, abbs_df$Franchise)]
head(OPtsPerGame)
```
```{r}
rm(abbs_df, page, Abbrevs, Abbs, FullNames)
save.image(file = 'PreLoadedData.RData')
```

