---
title: "Thanos Snaps the NBA"
author: "Samad Patel"
date: "8/16/2018"
header-includes: 
- \usepackage{graphicx}
output: pdf_document

---

Peter Parker is gone. We've had enough time to deal with it. Let's focus on the real issues - how would the NBA Playoffs have turned out if half of each roster was snapped? This module serves to investigate that. 

# Snapping the Players 

The first step is to collect the rosters of the playoffs teams, and then remove half of them. For the sake of argument, we will say LeBron James is Thanos (only due to the LeThanos memes at /r/NBA). He remains on the Cavs by default. 

```{r, echo = FALSE, warning=FALSE, message=FALSE}
library(readr)
# FULL ROSTERS 

# Cavs vs Pacers
cavaliers <- read_csv("~/Rosters/cavaliers.csv", skip = 8, col_names = c('Player'))
pacers <- read_csv("~/Rosters/pacers.csv", skip = 8, col_names = c('Player'))

# Celtics vs Bucks
celtics <- read_csv("~/Rosters/celtics.csv", skip = 8, col_names = c('Player'))
bucks <- read_csv("~/Rosters/bucks.csv", skip = 8, col_names = c('Player'))

# Raptors vs Wizards
wizards <- read_csv("~/Rosters/wizards.csv", skip = 8, col_names = c('Player'))
raptors <- read_csv("~/Rosters/raptors.csv", skip = 8, col_names = c('Player'))

# 76rs vs Heat
phil <- read_csv("~/Rosters/phil.csv", skip = 8, col_names = c('Player'))
heat <- read_csv("~/Rosters/heat.csv", skip = 8, col_names = c('Player'))
```

```{r, echo = FALSE}
myfunc <- function(x){
   return(gsub("\\\\.*", '', x))
}

cavaliers$Player <- apply(cavaliers[,1], FUN = myfunc, MARGIN = 2)
pacers$Player <- apply(pacers[,1], FUN = myfunc, MARGIN = 2)
celtics$Player <- apply(celtics[,1], FUN = myfunc, MARGIN = 2)
bucks$Player <- apply(bucks[,1], FUN = myfunc, MARGIN = 2)
wizards$Player <- apply(wizards[,1], FUN = myfunc, MARGIN = 2)
raptors$Player <- apply(raptors[,1], FUN = myfunc, MARGIN = 2)
phil$Player <- apply(phil[,1], FUN = myfunc, MARGIN = 2)
heat$Player <- apply(heat[,1], FUN = myfunc, MARGIN = 2)
```

With the exception of LeBron, each player has a 50% chance of remaining on the team. 

```{r}
# Do Bucks first to make sure it's correct
# Setting seed to 1 keeps LeBron (LeThanos) so we will keep it as such lol. 
set.seed(1)
snap <- function(df){
   return(df[sample(1:nrow(df), ceiling(nrow(df)/2)), ])
}

for (team in ls()[sapply(mget(ls()), is.data.frame)]){
   assign(team, snap(get(team)))
}

```

# Eastern Conference First Round

## Define Relevant Functions
```{r}
# Function to load in and clean names of players
myread <- function(filepath, skip_num){
   # Read in dataframe
   team <- read_csv(filepath, skip = skip_num)
   # Change name of first column to player
   colnames(team)[1] <- 'Player'
   # Clean up player column
   team$Player <- gsub('\\\\.*', '', team$Player)
   return(team)
}

# Function to calculate officiency rating 
ORTG <- function(team1, team2){
   FGA <- sum(team1$FGA, na.rm=T)
   OppFGA <- sum(team2$FGA, na.rm=T)
   
   FTA <- sum(team1$FTA, na.rm=T)
   OppFTA <- sum(team2$FTA, na.rm=T)
   
   ORB <- sum(team1$ORB, na.rm=T)
   OppORB <- sum(team2$ORB, na.rm=T)
      
   DRB <- sum(team1$DRB, na.rm=T)
   OppDRB <- sum(team2$DRB, na.rm=T)
   
   FG <- sum(team1$FG, na.rm=T)
   OppFG <- sum(team2$FG, na.rm=T)
   
   TOV <- sum(team1$TOV, na.rm=T)
   OppTOV <- sum(team2$TOV, na.rm=T)
   
   numerator <- 100*sum(team1$PTS)
   
   denominator <- (0.5 * ((FGA + 0.4 * FTA - 1.07 * 
                              (ORB / (ORB + OppDRB)) * (FGA - FG) + TOV) + 
                             (OppFGA + 0.4 * OppFTA - 1.07 * (OppORB / (OppORB + DRB)) *
                                 (OppFGA - OppFG) + OppTOV)))
   
   return(numerator/denominator)
}

# Function to calculate score 
scores <- function(home_OE, home_DE, away_OE, away_DE, home_pace, away_pace,
                   home_team_name, away_team_name){
  # Calculate adjusted efficiency based on being away or home 
  home_OE_adj <- home_OE * 1.015 # Gives home court advantage 
  home_DE_adj <- home_DE * .985
  
  away_OE_adj <- away_OE * .985
  away_DE_adj <- away_DE * 1.015
  
  # Calculate adjusted pace
  LA_pace <- 97.3 # Taken from basketballreference
  adj_pace <- (home_pace*away_pace)/LA_pace
  
  # Points per posession 
  LA_ORTG <- 106.3
  home_ppp <- (home_OE_adj*away_DE_adj) / LA_ORTG
  away_ppp <- (away_OE_adj*home_DE_adj) / LA_ORTG
  
  # Final Scores
  home_points <- floor((home_ppp*adj_pace)/100)
  away_points <- floor((away_ppp*adj_pace)/100)
  
  return(paste('Final: ', home_team_name, ' - ', home_points, ', ', away_team_name, ' - ', away_points, sep = ''))
}
```

## Round 1: Celtics Vs Bucks
### Game 1
```{r, message=FALSE, warning=FALSE, echo = FALSE}
# Load the initial team dataframes for game 1
team1 <- myread('~/Desktop/Celtics Vs Bucks/celtics_1.csv', skip_num = 7)
team2 <- myread('~/Desktop/Celtics Vs Bucks/bucks_1.csv', skip_num = 7)

# Keep only rows with non-snapped players
team1 <- team1[which(celtics$Player %in% team1$Player), ]
team2 <- team2[which(bucks$Player %in% team2$Player), ]

team1_ORTG <- ORTG(team1, team2)
team2_ORTG <- ORTG(team2, team1)

team1_DRTG <- (100.4/100.6)*100
team2_DRTG <- (106.8/99.1)*100

scores(team1_ORTG, team1_DRTG, team2_ORTG, team2_DRTG, 96.5, 96.5, 'Celtics', 'Bucks')
```

### Game 2
```{r, echo = FALSE, warning=FALSE, message=FALSE}
# Load the initial team dataframes for game 2
team1 <- myread('~/Desktop/Celtics Vs Bucks/celtics_2.csv', skip_num = 7)
team2 <- myread('~/Desktop/Celtics Vs Bucks/bucks_2.csv', skip_num = 7)

# Keep only rows with non-snapped players
team1 <- team1[which(celtics$Player %in% team1$Player), ]
team2 <- team2[which(bucks$Player %in% team2$Player), ]

team1_ORTG <- ORTG(team1, team2)
team2_ORTG <- ORTG(team2, team1)

team1_POS <- 99.1
team2_POS <- 100.6

team1_DRTG <- (100.4/team2_POS)*100
team2_DRTG <- (106.8/team1_POS)*100

scores(team1_ORTG, team1_DRTG, team2_ORTG, team2_DRTG, 92.5, 92.5, 'Celtics', 'Bucks')
```

### Game 3
```{r, echo = FALSE, warning=FALSE, message=FALSE}
team1 <- myread('~/Desktop/Celtics Vs Bucks/bucks_3.csv', skip_num = 7)
team2 <- myread('~/Desktop/Celtics Vs Bucks/celtics_3.csv', skip_num = 7)

# Keep only rows with non-snapped players
team1 <- team1[which(bucks$Player %in% team1$Player), ]
team2 <- team2[which(celtics$Player %in% team2$Player), ]

team1_ORTG <- ORTG(team1, team2)
team2_ORTG <- ORTG(team2, team1)

team2_POS <- 99.1
team1_POS <- 100.6

team1_OPA <- 106.8
team2_OPA <- 100.4

team1_DRTG <- (team1_OPA/team2_POS)*100
team2_DRTG <- (team2_OPA/team1_POS)*100

scores(team1_ORTG, team1_DRTG, team2_ORTG, team2_DRTG, 87.7, 87.7, 'Bucks', 'Celtics')
```

### Game 4
```{r, warning=FALSE, echo=FALSE, message=FALSE}
team1 <- myread('~/Desktop/Celtics Vs Bucks/bucks_4.csv', skip_num = 7)
team2 <- myread('~/Desktop/Celtics Vs Bucks/celtics_4.csv', skip_num = 7)

# Keep only rows with non-snapped players
team1 <- team1[which(bucks$Player %in% team1$Player), ]
team2 <- team2[which(celtics$Player %in% team2$Player), ]

team1_ORTG <- ORTG(team1, team2)
team2_ORTG <- ORTG(team2, team1)

team2_POS <- 99.1
team1_POS <- 100.6

team1_DRTG <- (106.8/team2_POS)*100
team2_DRTG <- (100.4/team1_POS)*100

scores(team1_ORTG, team1_DRTG, team2_ORTG, team2_DRTG, 88.3, 88.3, 'Bucks', 'Celtics')
```

### Game 5
```{r, warning=FALSE, message=FALSE, echo = FALSE}
# Load the initial team dataframes for game 2
team1 <- myread('~/Desktop/Celtics Vs Bucks/celtics_5.csv', skip_num = 7)
team2 <- myread('~/Desktop/Celtics Vs Bucks/bucks_5.csv', skip_num = 7)

# Keep only rows with non-snapped players
team1 <- team1[which(celtics$Player %in% team1$Player), ]
team2 <- team2[which(bucks$Player %in% team2$Player), ]

team1_ORTG <- ORTG(team1, team2)
team2_ORTG <- ORTG(team2, team1)

team1_POS <- 99.1
team2_POS <- 100.6

team1_DRTG <- (100.4/team2_POS)*100
team2_DRTG <- (106.8/team1_POS)*100

scores(team1_ORTG, team1_DRTG, team2_ORTG, team2_DRTG, 92.5, 92.5, 'Celtics', 'Bucks')
```

## Round 1: Cavaliers Vs Pacers
```{r, message=FALSE}

```

